Dismal Code: Studying the Evolution of Security Bugs

### 2013-03-23 docs/evol.tex
minor corrections

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The resulting correlation plot can be seen in
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from those involving the {\it Security Low} category,
due to the small number of bugs in that category (19). The results
show then that bugs do flock together: we do not find projects with
only a certain kind of bug; bugs come upon projects in swarms of
different kinds. Since the correlations with the {\it Security High}
category are particularly high, the presence of other bugs should be a
strong indicator to have a better look at security aspects of code.
\begin{table}
  \begin{threeparttable}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \begin{tablenotes}
      \footnotesize
      \item The matrix presents pairwise correlations between the
        following bug categories in order: Security High, Security
        Low, Style, Bad Practice, Correctness, MT Correctness,
        Performance, i18n, Experimental
    \end{tablenotes}
  \end{threeparttable}
\end{table}

>>>>

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from those involving the {\it Security Low} category,
due to the small number of bugs in that category (19). The results
show then that bugs do flock together: we do not find projects with
only a certain kind of bug; bugs come upon projects in swarms of
different kinds. Since the correlations with the {\it Security High}
category are particularly high, the presence of other bugs should be a
strong indicator to have a better look at security aspects of code.
\begin{table}
  \begin{threeparttable}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \begin{tablenotes}
      \footnotesize
      \item The matrix presents pairwise correlations between the
        following bug categories in order: Security High, Security
        Low, Style, Bad Practice, Correctness, MT Correctness,
        Performance, i18n, Experimental.
    \end{tablenotes}
  \end{threeparttable}
\end{table}
